A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-18 paper/paper.Rmd
caption for figure 7

```{r compare-subsets, fig.cap = "Comparison of original textbook example with refreshed data: (A) highest grade completed, (B) experience and (C) log wages", fig.width = 9, fig.height = 7, out.width = "100%", cache = FALSE}
```

>>>>

```{r compare-subsets, fig.cap = "Comparison of original and refreshed data: (A) highest grade completed, (B) experience and (C) log wages. Some difference in wages would be expected because the refreshed data is not inflation-adjusted, but the two sets are reasonably similar.", fig.width = 9, fig.height = 5, out.width = "100%", cache = FALSE}
```

### 2022-02-18 paper/paper.tex
caption for figure 7

\caption{Comparison of original textbook example with refreshed data: (A) highest grade completed, (B) experience and (C) log wages}\label{fig:compare-subsets}
\end{figure}

>>>>

\caption{Comparison of original and refreshed data: (A) highest grade completed, (B) experience and (C) log wages. Some difference in wages would be expected because the refreshed data is not inflation-adjusted, but the two sets are reasonably similar.}\label{fig:compare-subsets}
\end{figure}
